### 2020-12-05 paper/localpsf.tex
dirac comb dual notation may be confusing, but is needed for correctness

Our approximation is defined by:
\begin{itemize}
	\item how we compute the convolution kernels, $\varphi_i$, (Section \ref{sec:get_impulse_response})
	\item how we choose the points, $x_i$, (Section \ref{sec:choosing_sample_points}) and 
	\item what weighting functions $w_i$ that we use (Section \ref{sec:weighting_functions}). 
\end{itemize}
To briefly summarize, we compute one ``batch'' of $\varphi_i$'s by applying $\mathcal{A}$ to a sum of point sources, $\delta_{x_i},$ at many points $x_i$ (a ``Dirac comb''). That is, we compute
\begin{equation*}
	\eta = \sum_{i=1}^m A(~\cdot~, x_i) = \left\langle \mathcal{A}, \sum_{i=1}^m \delta_{x_i} \right\rangle^*.
\end{equation*}
Here $\sum_{i=1}^m \delta_{x_i}$ is the Dirac comb distribution, and $\left\langle \mathcal{A}, \sum_{i=1}^m \delta_{x_i} \right\rangle^*$ denotes the Riesz representation of the application of $\mathcal{A}$ to the Dirac comb. In computations, this amounts to computing $\boldsymbol{\eta} = \mathbf{M}^{-1}\mathbf{A} \mathbf{M}^{-1} \left(\sum_{i=1}^m \boldsymbol{\delta}_{x_i}\right)$, where $\boldsymbol{\eta}$, $\mathbf{A}$, and $\boldsymbol{\delta}_{x_i}$ are discretized versions of $\eta$, $A$, and $\delta_{x_i}$, respectively, and $\mathbf{M}$ is a mass matrix. The batch of points $x_i$ are chosen so that the support of $\left\langle \mathcal{A}, \delta_{x_i}\right\rangle^*$ and the support of $\left\langle \mathcal{A}, \delta_{x_j}\right\rangle^*$ do not overlap (or do not overlap much) if $i \neq j$. Since the impulse responses do not overlap, we may post-process $\eta$ to recover $\varphi_i$ for all of the points $x_i$ in the batch---by applying $\mathcal{A}$ to one vector, we recover many $\varphi_i$. This is illustrated in Figure FIG. The process is repeated to get more batches of $\varphi_i$'s, until the approximation is sufficiently accurate or a maximum number of sample points is reached. The supports of the impulse responses $\left\langle \mathcal{A}, \delta_{x}\right\rangle^*$ are estimated a-priori, for all $x \in \Omega$ simultaneously, via a procedure (described in Section \ref{eq:mean_and_covariance_estimation}) that involves applying $\mathcal{A}^T$ to a small number of constant, linear, and quadratic functions. This procedure is the only part of the paper that requires non-negativity of the integral kernel. The functions $w_i$ are the smoothest functions, in a least-squares sense, that interpolate the points $x_i$. Computing the functions $w_i$ require solving two Poisson PDEs per weighting function, and these PDE solves are done cheaply using multigrid.

>>>>

Our approximation is defined by:
\begin{itemize}
	\item how we compute the convolution kernels, $\varphi_i$, (Section \ref{sec:get_impulse_response})
	\item how we choose the points, $x_i$, (Section \ref{sec:choosing_sample_points}) and 
	\item what weighting functions, $w_i$, that we use (Section \ref{sec:weighting_functions}). 
\end{itemize}
Briefly, we compute one ``batch'' of $\varphi_i$'s by applying $\mathcal{A}$ to a sum of point sources, $\delta_{x_i},$ at many points $x_i$ (a ``Dirac comb''). That is, we compute
\begin{equation*}
	\eta = \sum_{i=1}^m A(~\cdot~, x_i) = \left\langle \mathcal{A}, \sum_{i=1}^m \delta_{x_i} \right\rangle^*.
\end{equation*}
Here $\sum_{i=1}^m \delta_{x_i}$ is the Dirac comb distribution, and $\left\langle \mathcal{A}, \sum_{i=1}^m \delta_{x_i} \right\rangle^*$ denotes the Riesz representation of the application of $\mathcal{A}$ to the Dirac comb. In computations, this amounts to computing $\boldsymbol{\eta} = \mathbf{M}^{-1}\mathbf{A} \mathbf{M}^{-1} \left(\sum_{i=1}^m \boldsymbol{\delta}_{x_i}\right)$, where $\boldsymbol{\eta}$, $\mathbf{A}$, and $\boldsymbol{\delta}_{x_i}$ are discretized versions of $\eta$, $A$, and $\delta_{x_i}$, respectively, and $\mathbf{M}$ is a mass matrix. The batch of points $x_i$ are chosen so that the support of $\left\langle \mathcal{A}, \delta_{x_i}\right\rangle^*$ and the support of $\left\langle \mathcal{A}, \delta_{x_j}\right\rangle^*$ do not overlap (or do not overlap much) if $i \neq j$. Since the impulse responses do not overlap, we may post-process $\eta$ to recover $\varphi_i$ for all of the points $x_i$ in the batch---by applying $\mathcal{A}$ to one distribution, we recover many $\varphi_i$. This is illustrated in Figure FIG. The process is repeated to get more batches of $\varphi_i$'s, until the approximation is sufficiently accurate or a maximum number of sample points is reached. The supports of the impulse responses $\left\langle \mathcal{A}, \delta_{x}\right\rangle^*$ are estimated a-priori, for all $x \in \Omega$ simultaneously, via a procedure (described in Section \ref{eq:mean_and_covariance_estimation}) that involves applying $\mathcal{A}^T$ to a small number of constant, linear, and quadratic functions. This procedure is the only part of the paper that requires non-negativity of the integral kernel. The functions $w_i$ are the smoothest functions, in a least-squares sense, that interpolate the points $x_i$. Computing the functions $w_i$ require solving two Poisson PDEs per weighting function, and these PDE solves are done cheaply using multigrid.
